LAGOS lake depth

### 2020-02-28 figures/01_contrasts.Rmd
typo fix

gg_shape <- cowplot::plot_grid(
  gg_depth_shape_class + ggtitle("Depth (m)") + theme_opts,
  gg_area_shape_class + ggtitle("Area (ha)") + theme_opts, 
  gg_area_shape_class + ggtitle("Inlake slope (m/m)") + theme_opts, 
  gg_area_shape_class + ggtitle("Deepest point distance (m)") + theme_opts, 
  nrow = 1)

>>>>

gg_shape <- cowplot::plot_grid(
  gg_depth_shape_class + ggtitle("Depth (m)") + theme_opts,
  gg_area_shape_class + ggtitle("Area (ha)") + theme_opts, 
  gg_slope_shape_class + ggtitle("Inlake slope (m/m)") + theme_opts, 
  gg_dist_shape_class + ggtitle("Deepest point distance (m)") + theme_opts, 
  nrow = 1)
